---
title: '289'
output: html_document
date: "2023-02-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

```{r message=FALSE, warning=FALSE}
library(tidyverse)
```

```{r}
fbref_offense <- read_csv("data/fbref_offense_clean.csv") %>% select(-c(1))
fbref_defense <- read_csv("data/fbref_defense_clean.csv") %>% select(-c(1))
fbref_comb <- rbind(fbref_offense, fbref_defense)

fbref_comb <- fbref_comb %>% separate(height, into = c("feet", "inch"), sep = "-") %>%
  mutate(height = (as.numeric(feet) * 12) + as.numeric(inch)) %>% select(-feet, -inch) %>% select(year, player, position, age, school, height, wt, forty, vertical, bench_reps, broad_jump, three_cone, shuttle, drafted) %>%
  rename(weight = wt) %>% separate(drafted, into = c("Drafted By", "Round", "Pick", "Year2"), sep = "/") %>%
  select(-Year2) %>% mutate(Round = parse_number(Round), Pick = parse_number(Pick)) %>%
  select(position, Round, forty, vertical, bench_reps, broad_jump, three_cone, shuttle)
```

This code creates a scatter plot using ggplot. The x-axis represents shuttle times and the y-axis represents forty times. The geom_point() function adds the individual data points to the plot.
```{r}
ggplot(fbref_comb, aes(x = shuttle, y = forty)) +
  geom_point() 
```

To investigate trends of scatter plots it is often good to plot a line of best fit, the geom_smooth() function adds a line of best fit to the plot. In this example we are using the linear line method.
```{r}
ggplot(fbref_comb, aes(x = shuttle, y = forty)) +
  geom_point() +
  geom_smooth(method = "lm")
```

Suppose we're interested in observing how the timing data differs across player positions. Here are two distinct approaches to include a color-coded legend that represents the "position" variable in the dataset.
```{r}
ggplot(fbref_comb, aes(x = shuttle, y = forty, color = position)) +
  geom_point() 

ggplot(fbref_comb, aes(x = shuttle, y = forty)) +
  geom_point() +
  geom_smooth(se = F, aes(color = position), method = "lm")
```

__Question:__ Describe the challenges associated with interpreting these plots that illustrate the performance of various positions in terms of the shuttle and forty. 

__Question:__ Suggest an idea to improve the visibility of the trends.


Facet graphs allow us to create multiple plots, each displaying a subset of the data, and compare trends and patterns across different groups or categories in a dataset.By breaking the data into smaller subsets, we can more easily observe patterns and relationships between subsets of the data that might not be visible in a single plot. Faceting also allows us to create a series of plots quickly and efficiently, making it easy to explore different aspects of the data without needing to create individual plots for each category or subset of the data.


The facet_wrap() function allows us to create a grid of multiple plots based on a categorical variable, in this case "position". This gives us a more detailed view of how different positions perform in terms of shuttle and forty.
```{r}
ggplot(fbref_comb, aes(x = shuttle, y = forty)) +
  geom_point() +
  geom_smooth(method = "lm") + 
  facet_wrap(~position)
```

It is now much easier to see the forty and shuttle trends of each position.

Another feature of the facet graphs is that we can group by two subsets. In this case we create a grid of plots based on the year and draft round, with each plot displaying the forty and shuttle trends for a specific combination of year and round (here we are using years greater than 2018). The ncol parameter is used to specify the number of columns in the grid, with a value of 8 resulting in 8 plots per row.
```{r}
ggplot(fbref_comb %>% filter(year > 2018), aes(x = shuttle, y = forty)) +
  geom_point() +
  geom_smooth(method = "lm") + 
  facet_wrap(year ~ Round, ncol = 8)
```


__Task__


In this excersise we want to compare players who will likely be matchuped up against each other in a game. We are going to be comparing Wide Recievers vs Defensive Backs. At the same time we want to compare the different forty and vertical scores between a 1st and 7th round pick.

The dataset you have been given gives specific positions for each player. Modify the position variable that generalizes the defensive back position more broadly following this guide:

CB, S --> DB

Create plots based on WR and DB grouped by their draft round (1 & 7) to compare relationships between vertical and broad_jump scores. Make the plot all in one row 


#solution:
```{r}
excersisesoultion <- fbref_comb %>% 
  mutate(position = case_when(position == "CB" ~ "DB",
                              position == "S" ~ "DB",
                              TRUE ~ position)) %>%
  filter(position == "WR" | position == "DB" ) %>%
  filter(Round == 1 | Round == 7) 

ggplot(excersisesoultion, aes(x = forty, y = vertical)) +
  geom_point() +
  facet_wrap(position ~ Round, nrow = 1) +
  geom_smooth(method = "lm")
  
```


